Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-06 main.Rmd
fixing renv package dependencies

```{r write-bib, eval = FALSE}
write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr"), file = "rpkgs.bib")
```

>>>>

```{r write-bib, eval = FALSE}
write_bib(c("rmarkdown", "bookdown", "rticles", "knitr", "ggplot2", "dplyr", "tsibble", "gravitas", "ggpubr", "kableExtra", "magrittr", "readr", "lubridate", "renv","archive"), file = "rpkgs.bib")
```
